On Secure Delegation of SampBQP with a Classical Client

### 2020-01-24 preliminaries.tex
Update IND-CPA for protocols

\begin{dfn}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$.
	Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

\begin{rmk}
	\Ethan{Maybe something about this being (hopefully) equivalent to simulator-based security?}
\end{rmk}

>>>>

\begin{dfn}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State The challenge picks $b\in\set{0,1}$ at random
		\If{b=1}
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\Else
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\EndIf
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}
